Modeling Human Interactions in Collaborative Interactive Evolutionary Computation

### 2017-02-02 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-body.tex
Erasing addressed comments and some fixes

\subsection{PostgreSQL}
  The PostgreSQL relational database system, is also employed because user sessions and authentication,
  as well as dynamic web pages are handled directly by the Django web framework \cite{garcia2013evospace}.

@@

\subsection{Fitness Assignment}
\label{sec:assignment}
The ES-I % You should use always the same acronym, not start using it
         % here - JJ 
         % Done -Mario
 platform employs a collaborative methodology for performing fitness
 assignment. Several registered users assign a quality assessment to a single
phenotype and then an aggregated fitness value is calculated,
depending on the rating (from 1 to 5 stars) of each particular user,  % how do you define
                                % "taste"? - JJ
                                % Using actions
resulting in a many-to-many relationship between users and
phenotypes. 
 %scored by them? - JJ 
Other components or users of the systems can % formerly published methods? Other researchers? - JJ
% Corrected -Mario
query this user-phenotype relation to extract relevant
knowledge about the process and the population, for instance showing the
most popular phenotype, or the the user with more participation 
\cite{picbreeder}.
In order to do this, metadata about phenotypes % metadata better? - JJ Yes -Mario
must be permanently stored, even
if they are no longer in the active population.

\subsection{Collaboration}
\label{sec:col}
Users need to authenticate themselves to the system using their
Facebook account. In that sense, some users might not be interested
either because they do not want to give that information or simply because
they do not use that particular social network. Even as we might lose
some users that way, the additional information we obtain for scoring
phenotypes more than compensates for that. % Added this, check it
                                % out.  
                                % Ok! - Mario (and knowing how much more is future work)
After entering the web application by using their Facebook account,
users can collaborate with their Facebook friends, 
sharing those phenotypes they like, or by taking phenotypes
from their friend's collections by using the web interface depicted 
in Figure \ref{fig:web}.
At the top left corner a list of Facebook friends is presented
to encourage users to interact with the system. In the central 
\emph{ Wall } area, a phenotype sampled from the population that is
being evolved via the evolutionary algorithm 
is shown to the user.
Here, the user can interact with the system in two ways.
First, he can assign a rating % Why don't you use other
                                % thing instead of quality? We are not
                                % talking about quality, but about
                                % tastes or similar - JJ
                                % is rating Ok? 
 to the phenotype using
a five star rating system or,
additionally, a user can choose to add an image to one of their \emph{Collections}.
A collection is a special folder that stores those phenotypes a user likes and wishes
to save. After the user finishes interacting with the phenotype
on the Wall, he can choose to retrieve a new one from the population.
At the left hand side of \ref{fig:web}, the web page shows the \emph{Collections} section.
The user can create several collections, to group and organize his favorite 
artifacts. Moreover, users can browse the content of each collection and from
there share images through their social network.
When a user hovers the cursor over a phenotypes a pop-up pane shows how many users have
liked the phenotype. The pane also includes a link to the phenotype's 
details, the parents, genetic operators that created it, and genealogy
information. This makes the assignment of fitness through the rating
system a {\em social} activity, pursuing the objective of this work,
which is to increase engagement of the users.
\subsubsection{Graph Model}

@@

  % The authors would also like to thank the anonymous referees for
  % their valuable comments and helpful suggestions. The work is
  % supported by the \grantsponsor{GS501100001809}{National Natural
  %   Science Foundation of
  %   China}{http://dx.doi.org/10.13039/501100001809} under Grant
  % No.:~\grantnum{GS501100001809}{61273304}
  % and~\grantnum[http://www.nnsf.cn/youngscientsts]{GS501100001809}{Young
  %   Scientsts' Support Program}.

>>>>

\subsection{PostgreSQL}
  The PostgreSQL relational database system is also employed because user sessions and authentication,
  as well as dynamic web pages are handled directly by the Django web
  framework \cite{garcia2013evospace}. % these implementations details
                                % could go if needed.

@@

\subsection{Fitness Assignment}
\label{sec:assignment}
% changed to this, because I understand it does not always work that
% way - JJ
The ES-I platform has been programmed to employ a collaborative methodology for performing fitness
 assignment. Several registered users assign a quality assessment to a single
phenotype and then an aggregated fitness value is calculated,
depending on the rating (from 1 to 5 stars) by each particular user,  % how do you define
                                % "taste"? - JJ
                                % Using actions
resulting in a many-to-many relationship between users and
phenotypes. 
 %scored by them? - JJ 
Other components or users of the systems can 
query this user-phenotype relation to extract relevant
knowledge about the process and the population, for instance showing the
most popular phenotype, or the the user with more participation 
\cite{picbreeder}.
In order to do this, metadata about phenotypes 
must be permanently stored, even
if they are no longer in the active population.

\subsection{Collaboration}
\label{sec:col}
Users need to authenticate themselves to the system using their
Facebook account. In that sense, some users might not be interested
either because they do not want to give that information or simply because
they do not use that particular social network. Even as we might lose
some users that way, the additional information we obtain for scoring
phenotypes more than compensates for that. % Added this, check it
                                % out.  
                                % Ok! - Mario (and knowing how much more is future work)
After entering the web application by using their Facebook account,
users can collaborate with their Facebook friends, 
sharing those phenotypes they like, or by taking phenotypes
from their friend's collections by using the web interface depicted 
in Figure \ref{fig:web}.
At the top left corner a list of Facebook friends is presented
to encourage users to interact with the system. In the central 
\emph{ Wall } area, a phenotype sampled from the population that is
being evolved via the evolutionary algorithm 
is shown to the user.
Here, the user can interact with the system in two ways.
First, he can assign a rating % Why don't you use other
                                % thing instead of quality? We are not
                                % talking about quality, but about
                                % tastes or similar - JJ
                                % is rating Ok?
% Rating is probably OK. 
 to the phenotype using
a five star rating system or,
additionally, a user can choose to add an image to one of their \emph{Collections}.
A collection is a special folder that stores those phenotypes a user likes and wishes
to save. After the user finishes interacting with the phenotype
on the Wall, he can choose to retrieve a new one from the population.
At the left hand side of \ref{fig:web}, the web page shows the \emph{Collections} section.
The user can create several collections, to group and organize his favorite 
artifacts. Moreover, users can browse the content of each collection and from
there share images through their social network.
When a user hovers the cursor over a phenotypes a pop-up pane shows how many users have
liked the phenotype. The pane also includes a link to the phenotype's 
details, the parents, genetic operators that created it, and genealogy
information. This makes the assignment of fitness through the rating
system a {\em social} activity, pursuing the objective of this work,
which is to increase engagement of the users.
\subsubsection{Graph Model}

@@

  % The authors would also like to thank the anonymous referees for
  % their valuable comments and helpful suggestions. The work is
  % supported by the \grantsponsor{GS501100001809}{National Natural
  %   Science Foundation of
  %   China}{http://dx.doi.org/10.13039/501100001809} under Grant
  % No.:~\grantnum{GS501100001809}{61273304}
  % and~\grantnum[http://www.nnsf.cn/youngscientsts]{GS501100001809}{Young
  % Scientsts' Support Program}.
  Reserved\\
  Space\\
  for\\
  Acks
